Improving Adaptive Seamless Designs through Bayesian optimization

### 2021-06-07 main.tex
appendix
cleanup boxplots
opt eps and thresh plots

% %%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
% \clearpage
% \begin{center}
% \textbf{\large Supplemental Materials: \newtitle}
% \end{center}
% \FloatBarrier
% %%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
% %%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
% \setcounter{equation}{0}
% \setcounter{figure}{0}
% \setcounter{table}{0}
% \setcounter{page}{1}
% \makeatletter
% \renewcommand{\theequation}{S\arabic{equation}}
% \renewcommand{\thefigure}{S\arabic{figure}}
% \renewcommand{\thetable}{S\arabic{table}}
% \renewcommand{\bibnumfmt}[1]{[S#1]}
% %%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%

% \input{generated/tables/table_best.tex}

% \begin{figure}[htb]
% \centering
% \includegraphics[width=\linewidth]{generated/figures/plot_opt_path.pdf}
% \caption{%
%   Optimization curves of each optimization run and the mean of all runs drawn as a black line.
%   }
% \label{fig:plot_opt_path} 
% \end{figure}

>>>>

%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
\clearpage
\begin{center}
\textbf{\large Supplemental Materials: \newtitle}
\end{center}
\FloatBarrier
%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{generated/figures/plot_opt_path.pdf}
\caption{%
  Optimization progress for \emph{BO}: Best outcome found so far for each iteration, in comparison to the best outcome found in the grid search, for all effect sets and all values of $n_{\text{total}}$.
}
\label{fig:plot_opt_path} 
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\linewidth]{generated/figures/plot_appendix_opt_epsilon.pdf}%
\includegraphics[width=0.5\linewidth]{generated/figures/plot_appendix_opt_thresh.pdf}
\caption{%
  This figure shows the location of the optimal values of $\varepsilon$ and $\tau$ for their respective rules obtained through the \emph{Grid} search, averaged across the 20 stochastic replications.
  It indicates that the search space for $r$ and $\varepsilon$ or $\tau$ is big enough but that each should be optimized on a $log$-scale.
  The color indicates the value of $y$, with \emph{red} beeing good.
  $y$-values are scaled for each single plot and cannot be compared across experiments.
  The best points are indicated through a white dot.
}
\label{fig:plot_opt_eps_thresh} 
\end{figure}
